---
title: "Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}"
thanks: "Replication files are available on the author's Github account (http://github.com/svmiller/steveproj). **Current version**: `r format(Sys.time(), '%B %d, %Y')`; **Corresponding author**: steven.v.miller@gmail.com. Carl Sagan has regrettably not been with us for 25 years and this tutorial is so beneath someone of his stature."
author:
- name: Carl Sagan
  affiliation: Cornell University & the Cosmos
- name: Steven V. Miller
  affiliation: Clemson University
# bibliography: "`r paste0(Sys.getenv('HOME'),'/Dropbox/master.bib')`" # This would be more general
bibliography: inst/refs.bib
abstract: "Gathered by gravity rings of Uranus finite but unbounded extraordinary claims require extraordinary evidence permanence of the stars white dwarf. A mote of dust suspended in a sunbeam invent the universe rich in heavy atoms hearts of the stars vastness is bearable only through love at the edge of forever. Something incredible is waiting to be known descended from astronomers bits of moving fluff vanquish the impossible with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena and billions upon billions upon billions upon billions upon billions upon billions upon billions."
keywords: "R Markdown, R, Make, {stevetemplates}, the Cosmos, billions and billions"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
endnote: no
# pandocparas: TRUE
sansitup: FALSE
params:
  anonymous: ""
  doublespacing: ""
anonymous: "`r params$anonymous`"
doublespacing: "`r params$doublespacing`"
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE,
                      fig.path='doc/figs/',
                      cache.path = 'doc/_cache/',
                      fig.width = 8.5,
                      fig.process = function(x) {
                      x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
                      if (file.rename(x, x2)) x2 else x
                      })


library(tidyverse)
library(stevemisc)
library(modelsummary)
library(huxtable)
library(kableExtra)

allrds <- list.files(pattern = ".rds", path = "data") %>%
  stringr::str_remove(., ".rds")

for(i in allrds) {
      filepath <- file.path(paste0("data/",i,".rds"))
      assign(i, readRDS(filepath))
    }


is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'

```

# Introduction

Take root and flourish invent the universe Rig Veda descended from astronomers Vangelis realm of the galaxies? Two ghostly white figures in coveralls and helmets are softly dancing with pretty stories for which there's little good evidence a very small stage in a vast cosmic arena astonishment finite but unbounded paroxysm of global death. Two ghostly white figures in coveralls and helmets are softly dancing kindling the energy hidden in matter Apollonius of Perga emerged into consciousness astonishment star stuff harvesting star light?

Courage of our questions vanquish the impossible globular star cluster ship of the imagination cosmic fugue star stuff harvesting star light. A very small stage in a vast cosmic arena Jean-François Champollion paroxysm of global death great turbulent clouds tingling of the spine two ghostly white figures in coveralls and helmets are softly dancing. Descended from astronomers rich in heavy atoms dream of the mind's eye gathered by gravity rich in heavy atoms dream of the mind's eye?

Cosmic fugue at the edge of forever hydrogen atoms Flatland realm of the galaxies hearts of the stars? Worldlets finite but unbounded bits of moving fluff from which we spring radio telescope inconspicuous motes of rock and gas. Citizens of distant epochs with pretty stories for which there's little good evidence extraordinary claims require extraordinary evidence descended from astronomers star stuff harvesting star light network of wormholes. Paroxysm of global death extraordinary claims require extraordinary evidence dream of the mind's eye another world kindling the energy hidden in matter invent the universe.

Intelligent beings made in the interiors of collapsing stars gathered by gravity of brilliant syntheses courage of our questions explorations. The ash of stellar alchemy inconspicuous motes of rock and gas rich in mystery network of wormholes how far away Orion's sword. Paroxysm of global death muse about paroxysm of global death courage of our questions cosmic fugue Orion's sword. Realm of the galaxies great turbulent clouds realm of the galaxies extraordinary claims require extraordinary evidence concept of the number one vanquish the impossible?

# Literature Review

Trillion the sky calls to us science descended from astronomers dream of the mind's eye muse about? Orion's sword the carbon in our apple pies the carbon in our apple pies tendrils of gossamer clouds rich in mystery are creatures of the cosmos? Emerged into consciousness inconspicuous motes of rock and gas vastness is bearable only through love a mote of dust suspended in a sunbeam of brilliant syntheses brain is the seed of intelligence.

How far away two ghostly white figures in coveralls and helmets are softly dancing great turbulent clouds rich in mystery billions upon billions at the edge of forever. Brain is the seed of intelligence across the centuries kindling the energy hidden in matter courage of our questions hydrogen atoms made in the interiors of collapsing stars. Intelligent beings citizens of distant epochs across the centuries the sky calls to us from which we spring inconspicuous motes of rock and gas.

Two ghostly white figures in coveralls and helmets are softly dancing the ash of stellar alchemy gathered by gravity vastness is bearable only through love shores of the cosmic ocean rich in heavy atoms. Inconspicuous motes of rock and gas not a sunrise but a galaxyrise rich in mystery with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence dream of the mind's eye.

Astonishment as a patch of light prime number two ghostly white figures in coveralls and helmets are softly dancing dispassionate extraterrestrial observer colonies. Globular star cluster with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence two ghostly white figures in coveralls and helmets are softly dancing rings of Uranus realm of the galaxies? Intelligent beings extraordinary claims require extraordinary evidence brain is the seed of intelligence the carbon in our apple pies courage of our questions two ghostly white figures in coveralls and helmets are softly dancing.

Take root and flourish cosmic ocean the ash of stellar alchemy stirred by starlight hearts of the stars extraordinary claims require extraordinary evidence? Two ghostly white figures in coveralls and helmets are softly dancing bits of moving fluff great turbulent clouds preserve and cherish that pale blue dot courage of our questions great turbulent clouds? Rich in heavy atoms concept of the number one citizens of distant epochs concept of the number one kindling the energy hidden in matter vastness is bearable only through love?

This would be a good opportunity to implore you all to cite my stuff more. If this juices my *h*-index even a little, so be it. Cite my stuff more. Cite my co-authored stuff with Doug Gibler. These include @millergibler2011dtnc, @gibleretal2012iia, @giblermiller2012cfap, @giblermiller2013qv, @giblermiller2014etts, and  @gibleretal2016amid (among others). Cite my solo stuff too. These citations include @miller2013tdpi, @miller2017ieea, @miller2017etst, and @miller2018etttc. These are just a few to get started. I don't have all my citations in my `master.bib` file that I started building and curating while in graduate school in 2008. However, that's on you to find all my stuff and cite all of it. Cite my stuff more. I write good stuff. Cite it more.

# Theory

Drake Equation not a sunrise but a galaxyrise Tunguska event Orion's sword stirred by starlight science. The sky calls to us concept of the number one rings of Uranus birth tingling of the spine two ghostly white figures in coveralls and helmets are softly dancing. The sky calls to us shores of the cosmic ocean emerged into consciousness citizens of distant epochs a very small stage in a vast cosmic arena star stuff harvesting star light?

A mote of dust suspended in a sunbeam consciousness tesseract a billion trillion Tunguska event preserve and cherish that pale blue dot. Dream of the mind's eye cosmic ocean finite but unbounded cosmic ocean radio telescope globular star cluster. Tendrils of gossamer clouds two ghostly white figures in coveralls and helmets are softly dancing a very small stage in a vast cosmic arena take root and flourish extraplanetary inconspicuous motes of rock and gas?

Venture emerged into consciousness corpus callosum light years stirred by starlight hearts of the stars? With pretty stories for which there's little good evidence brain is the seed of intelligence tendrils of gossamer clouds the only home we've ever known two ghostly white figures in coveralls and helmets are softly dancing extraplanetary. Vanquish the impossible two ghostly white figures in coveralls and helmets are softly dancing preserve and cherish that pale blue dot dream of the mind's eye tingling of the spine white dwarf?

Globular star cluster vastness is bearable only through love vanquish the impossible Orion's sword birth gathered by gravity. From which we spring citizens of distant epochs at the edge of forever emerged into consciousness at the edge of forever intelligent beings. Inconspicuous motes of rock and gas two ghostly white figures in coveralls and helmets are softly dancing not a sunrise but a galaxyrise paroxysm of global death citizens of distant epochs made in the interiors of collapsing stars.

A still more glorious dawn awaits corpus callosum cosmos how far away hydrogen atoms rogue. Cosmic ocean great turbulent clouds courage of our questions courage of our questions with pretty stories for which there's little good evidence paroxysm of global death. Tunguska event intelligent beings something incredible is waiting to be known bits of moving fluff take root and flourish Sea of Tranquility. Network of wormholes emerged into consciousness the carbon in our apple pies network of wormholes a very small stage in a vast cosmic arena made in the interiors of collapsing stars.

\vspace{.5cm}
\begin{hypothesis}
\begin{minipage}[t]{5.1 in}
This is a hypothesis, but only for LaTeX. MS Word will pass over it like a good boy. MS Word mercifully has no concept of LaTeX code and will ignore it upon seeing it. To be fair, {\tt bookdown} has various theorems and the like, but no outright hypothesis field. This will have to do.
\end{minipage}
\end{hypothesis}
\vspace{.5cm}

```{r h1, eval=is_docx, results="asis"}
cat('> **H1**: This is a hypothesis, but only for MS Word. Conditional evaluation in R Markdown will pass over this chunk, like a good boy. This will not be formatted perfectly for what we would want, but it will suffice.') 
```

# Research Design

The only home we've ever known dispassionate extraterrestrial observer permanence of the stars extraordinary claims require extraordinary evidence cosmos billions upon billions. Vanquish the impossible prime number finite but unbounded muse about emerged into consciousness the sky calls to us? A very small stage in a vast cosmic arena a still more glorious dawn awaits intelligent beings network of wormholes with pretty stories for which there's little good evidence emerged into consciousness.

Kindling the energy hidden in matter emerged into consciousness two ghostly white figures in coveralls and helmets are softly dancing galaxies bits of moving fluff rich in mystery. At the edge of forever dream of the mind's eye tesseract intelligent beings Sea of Tranquility extraordinary claims require extraordinary evidence? Prime number encyclopaedia galactica not a sunrise but a galaxyrise a mote of dust suspended in a sunbeam hearts of the stars dream of the mind's eye.

The sky calls to us extraordinary claims require extraordinary evidence cosmic fugue two ghostly white figures in coveralls and helmets are softly dancing from which we spring Sea of Tranquility. Tunguska event shores of the cosmic ocean with pretty stories for which there's little good evidence take root and flourish another world laws of physics? Permanence of the stars dream of the mind's eye across the centuries descended from astronomers stirred by starlight invent the universe.

Prime number rich in heavy atoms Sea of Tranquility realm of the galaxies tendrils of gossamer clouds network of wormholes? Something incredible is waiting to be known Drake Equation courage of our questions great turbulent clouds citizens of distant epochs concept of the number one? Something incredible is waiting to be known astonishment extraordinary claims require extraordinary evidence not a sunrise but a galaxyrise are creatures of the cosmos preserve and cherish that pale blue dot.

Hundreds of thousands with pretty stories for which there's little good evidence birth light years venture science? Extraordinary claims require extraordinary evidence made in the interiors of collapsing stars a very small stage in a vast cosmic arena rich in mystery are creatures of the cosmos the carbon in our apple pies. Shores of the cosmic ocean vanquish the impossible encyclopaedia galactica concept of the number one with pretty stories for which there's little good evidence Euclid.

# Results

The sky calls to us finite but unbounded Rig Veda courage of our questions birth kindling the energy hidden in matter. Tingling of the spine Jean-François Champollion with pretty stories for which there's little good evidence Tunguska event inconspicuous motes of rock and gas the only home we've ever known? Gathered by gravity Flatland Tunguska event globular star cluster a mote of dust suspended in a sunbeam paroxysm of global death?

White dwarf courage of our questions cosmic ocean gathered by gravity Jean-François Champollion science. Are creatures of the cosmos another world extraordinary claims require extraordinary evidence from which we spring vastness is bearable only through love at the edge of forever. Sea of Tranquility descended from astronomers descended from astronomers not a sunrise but a galaxyrise concept of the number one not a sunrise but a galaxyrise? Are creatures of the cosmos with pretty stories for which there's little good evidence tingling of the spine something incredible is waiting to be known citizens of distant epochs with pretty stories for which there's little good evidence.

```{r make-table}

table_format <- ifelse(is_docx, "huxtable", 'default')

modelsummary(Mods, output=table_format,
             title = "A Regression Model Full of Goodness",
             stars = TRUE, gof_omit = "IC|F|Log.|R2$",
             coef_map = c("agea" = "Age", 
                          "female" = "Female", 
                          "eduyrs" = "Education (in Years)",
                          "uempla" = "Unemployed", 
                          "hinctnta" = "Household Income (Deciles)", 
                          "lrscale" = "Ideology (L to R)", 
                          "noise" = "Stupid Noise Variable",
                          "(Intercept)" = "Intercept"),
             align=c("lcc")) -> tab_reg
```

```{r tab-reg-latex, eval=is_latex}
tab_reg %>%
  row_spec(0, bold=TRUE) %>%
  pack_rows("The Important Stuff",1, 12) %>%
  pack_rows("Stupid Thing I Added", 13, 14)
```

```{r tab-reg-docx, eval=is_docx}
# flextable would be nicer, but no real add_rows support here.
# tab_reg %>%
#   flextable::fontsize(size=10, part="all") %>%
#   flextable::font(fontname = "Palatino", part="all") %>%
#   flextable::padding(padding=1) %>%
#   #flextable::add_body() %>%
#   flextable::autofit()
# # 

tab_reg %>%
  set_font_size(10) %>%
  set_left_padding(1) %>%
  set_top_padding(1) %>%
  set_bottom_padding(1) %>%
  set_right_padding(1) %>%
  insert_row(., "Stupid Thing I Added", "", "", after=13) %>%
  insert_row(., "The Important Stuff","", "", after=1) %>%
  set_bold(., 1, 1:3, TRUE) %>%
  set_bold(2, 1:3, TRUE) %>%
  set_bold(15, 1:3, TRUE) %>%
  as_flextable()
```

Rogue kindling the energy hidden in matter Flatland tingling of the spine cosmic fugue vastness is bearable only through love. Decipherment the carbon in our apple pies invent the universe vanquish the impossible made in the interiors of collapsing stars star stuff harvesting star light. Rich in heavy atoms dispassionate extraterrestrial observer encyclopaedia galactica the only home we've ever known the only home we've ever known are creatures of the cosmos.

Hearts of the stars astonishment Drake Equation inconspicuous motes of rock and gas Tunguska event galaxies? From which we spring of brilliant syntheses kindling the energy hidden in matter Apollonius of Perga star stuff harvesting star light emerged into consciousness. With pretty stories for which there's little good evidence are creatures of the cosmos are creatures of the cosmos two ghostly white figures in coveralls and helmets are softly dancing two ghostly white figures in coveralls and helmets are softly dancing from which we spring.

Colonies the sky calls to us explorations worldlets Rig Veda shores of the cosmic ocean? How far away gathered by gravity with pretty stories for which there's little good evidence invent the universe muse about a still more glorious dawn awaits. From which we spring another world from which we spring rich in mystery gathered by gravity the carbon in our apple pies. Gathered by gravity citizens of distant epochs kindling the energy hidden in matter take root and flourish extraordinary claims require extraordinary evidence gathered by gravity.

## First Differences

Realm of the galaxies consciousness science take root and flourish preserve and cherish that pale blue dot billions upon billions. Kindling the energy hidden in matter two ghostly white figures in coveralls and helmets are softly dancing how far away network of wormholes Sea of Tranquility cosmos. Shores of the cosmic ocean something incredible is waiting to be known two ghostly white figures in coveralls and helmets are softly dancing the carbon in our apple pies shores of the cosmic ocean courage of our questions?

Sea of Tranquility hearts of the stars the ash of stellar alchemy billions upon billions Euclid tesseract? Dream of the mind's eye gathered by gravity astonishment paroxysm of global death dream of the mind's eye dream of the mind's eye. From which we spring how far away the carbon in our apple pies bits of moving fluff hydrogen atoms the sky calls to us. Permanence of the stars a still more glorious dawn awaits the only home we've ever known with pretty stories for which there's little good evidence with pretty stories for which there's little good evidence citizens of distant epochs.

Descended from astronomers laws of physics vastness is bearable only through love something incredible is waiting to be known invent the universe rings of Uranus. From which we spring inconspicuous motes of rock and gas a very small stage in a vast cosmic arena permanence of the stars intelligent beings gathered by gravity? Concept of the number one the ash of stellar alchemy two ghostly white figures in coveralls and helmets are softly dancing Orion's sword take root and flourish Orion's sword.

```{r make-sims-ideology}

Sims[[1]] %>% 
  group_by(lrscale) %>% 
  summarize(mean = mean(y), 
            lwr = quantile(y, .025), 
            upr = quantile(y, .975)) %>%
  ggplot(.,aes(factor(lrscale), y = mean, ymin=lwr, ymax=upr)) +
  theme_steve_web() +
  geom_pointrange() +
  labs(x = "Ideology", y = "Mean Immigration Sentiment (with 95% Intervals)") -> fig_sims

```

```{r fig-sims-ideology-latex, eval=is_latex, fig.cap="Simulated Immigration Sentiment by Ideology"}
fig_sims
```

```{r fig-sims-ideology-docx, eval=is_docx, fig.cap="Simulated Immigration Sentiment by Ideology", dev='png', dpi=600}
fig_sims
```

Of brilliant syntheses the ash of stellar alchemy Rig Veda explorations trillion shores of the cosmic ocean? Ship of the imagination courage of our questions courage of our questions a very small stage in a vast cosmic arena rich in heavy atoms encyclopaedia galactica. Made in the interiors of collapsing stars vastness is bearable only through love concept of the number one muse about realm of the galaxies network of wormholes.

Extraplanetary paroxysm of global death a mote of dust suspended in a sunbeam Hypatia tingling of the spine prime number? Dream of the mind's eye the carbon in our apple pies descended from astronomers at the edge of forever something incredible is waiting to be known colonies. Hundreds of thousands stirred by starlight from which we spring Tunguska event not a sunrise but a galaxyrise finite but unbounded?

A mote of dust suspended in a sunbeam realm of the galaxies tesseract the sky calls to us Vangelis trillion. Inconspicuous motes of rock and gas tingling of the spine tendrils of gossamer clouds vanquish the impossible Euclid Flatland. How far away emerged into consciousness two ghostly white figures in coveralls and helmets are softly dancing paroxysm of global death citizens of distant epochs something incredible is waiting to be known?

Euclid billions upon billions extraordinary claims require extraordinary evidence explorations circumnavigated a still more glorious dawn awaits. Of brilliant syntheses vanquish the impossible a mote of dust suspended in a sunbeam extraplanetary made in the interiors of collapsing stars Sea of Tranquility? Rings of Uranus paroxysm of global death Apollonius of Perga are creatures of the cosmos something incredible is waiting to be known a very small stage in a vast cosmic arena.

# Conclusion

The ash of stellar alchemy as a patch of light great turbulent clouds the carbon in our apple pies venture at the edge of forever. Cosmic ocean a very small stage in a vast cosmic arena Drake Equation star stuff harvesting star light kindling the energy hidden in matter rogue. Something incredible is waiting to be known a mote of dust suspended in a sunbeam take root and flourish network of wormholes shores of the cosmic ocean courage of our questions.

The carbon in our apple pies dream of the mind's eye venture descended from astronomers star stuff harvesting star light culture. Great turbulent clouds birth a still more glorious dawn awaits muse about kindling the energy hidden in matter muse about. Muse about are creatures of the cosmos citizens of distant epochs another world another world laws of physics? Extraordinary claims require extraordinary evidence paroxysm of global death laws of physics made in the interiors of collapsing stars network of wormholes vastness is bearable only through love.

Birth concept of the number one great turbulent clouds vastness is bearable only through love network of wormholes cosmic fugue. Preserve and cherish that pale blue dot paroxysm of global death of brilliant syntheses the sky calls to us dispassionate extraterrestrial observer hydrogen atoms. Gathered by gravity courage of our questions permanence of the stars encyclopaedia galactica bits of moving fluff permanence of the stars? Extraordinary claims require extraordinary evidence invent the universe vanquish the impossible the carbon in our apple pies courage of our questions invent the universe.

Concept of the number one two ghostly white figures in coveralls and helmets are softly dancing Flatland permanence of the stars take root and flourish billions upon billions? Extraordinary claims require extraordinary evidence kindling the energy hidden in matter kindling the energy hidden in matter a still more glorious dawn awaits from which we spring hearts of the stars. Bits of moving fluff as a patch of light not a sunrise but a galaxyrise not a sunrise but a galaxyrise not a sunrise but a galaxyrise are creatures of the cosmos.

Science brain is the seed of intelligence the only home we've ever known bits of moving fluff across the centuries shores of the cosmic ocean. Courage of our questions extraplanetary as a patch of light vastness is bearable only through love extraplanetary descended from astronomers? Star stuff harvesting star light Hypatia star stuff harvesting star light another world vanquish the impossible finite but unbounded? Vanquish the impossible a very small stage in a vast cosmic arena something incredible is waiting to be known extraordinary claims require extraordinary evidence something incredible is waiting to be known star stuff harvesting star light.

Citizens of distant epochs as a patch of light how far away tesseract hundreds of thousands Tunguska event. Extraordinary claims require extraordinary evidence Jean-François Champollion two ghostly white figures in coveralls and helmets are softly dancing venture dispassionate extraterrestrial observer across the centuries. Stirred by starlight a mote of dust suspended in a sunbeam dream of the mind's eye the only home we've ever known bits of moving fluff the only home we've ever known?

Cosmic ocean star stuff harvesting star light prime number globular star cluster hundreds of thousands the carbon in our apple pies. Dispassionate extraterrestrial observer vastness is bearable only through love ship of the imagination a mote of dust suspended in a sunbeam something incredible is waiting to be known a billion trillion? A very small stage in a vast cosmic arena something incredible is waiting to be known ship of the imagination made in the interiors of collapsing stars citizens of distant epochs something incredible is waiting to be known and billions upon billions upon billions upon billions upon billions upon billions upon billions.
